# Centre for Accessibility

```{r}
#| label: setup
#| echo: false
#| message: false
library(conflicted)
library(dplyr)
conflicts_prefer(dplyr::filter)
library(forcats)
library(fs)
library(ggplot2)
library(glue)
library(gt)
library(gtsummary)
library(labelled)
library(plotly)
library(scales)
library(tidyr)

dir_walk(here::here("R"), source)
students <- load_students()
lab_requests <- load_lab_requests()
lab_counts <- load_lab_counts()
```

## FoS students registered with CfA

::::::: panel-tabset
### Program (plot)

::: {#program-vs-specialization}
I decided to collate the data by program and count a student in a combined specialization once for each program (for example, a student in "Combined Major in Computer Science, Biology" is counted once for "Computer Science" and once for "Biology".) See @tbl-students-by-specialization for a more granular view by specialization.
:::

{{< contents program-vs-specialization >}}

::: {#fig-students-by-program}
```{r}
#| label: students-by-program-plot
#| echo: false
students_by_program <- students |>
  select(program_one, program_two) |>
  pivot_longer(
    everything(),
    names_to = NULL,
    values_to = "program",
    values_drop_na = TRUE
  ) |>
  set_variable_labels(
    program = "Program"
  )

students_by_program |>
  render_lollipop_graph(program)
```

[Faculty of Science students registered with the Centre for Accessibility by program ($N = `{r} nrow(students)`$, but students in combined programs are counted double).]{#students-by-program}{{< contents students-by-program >}} Same data as in @tbl-students-by-program as a plot.
:::

### Program (table)

{{< contents program-vs-specialization >}}

::: {#tbl-students-by-program}
```{r}
#| label: students-by-program-table
#| echo: false
students_by_program |>
  tbl_summary(include = program)
```

{{< contents students-by-program >}} Same data as in @fig-students-by-program as a table.
:::

### Specialization

This table shows the unprocessed data, where the different combinations of "Major", "Honours" and "Combined" choices result in many different specializations.

::: {#tbl-students-by-specialization}
```{r}
#| label: students-by-specialization
#| echo: false
students |>
  mutate(
    program_of_study_name = replace_values(
      program_of_study_name,
      "Bachelor of Science (Vancouver)" ~ "First year B.Sc."
    )
  ) |>
  set_variable_labels(
    program_of_study_name = "Specialization"
  ) |>
  tbl_summary(include = program_of_study_name)
```

Faculty of Science students registered with the Centre for Accessibility by specialization.
:::
:::::::

## FoS students registered with CfA in laboratory courses

In general, requests for accomodations by FoS students in courses got all approved and the data contains no examples when a request was rejected.

:::::: panel-tabset
### Faculty-level

::: {#tbl-requests}
```{r}
#| label: requests
#| echo: false
lab_requests |>
  # filter(in_ubc_v_faculty_of_science) |>
  mutate(
    course_faculty = recode_values(
      in_ubc_v_faculty_of_science,
      TRUE ~ "FoS",
      FALSE ~ "non-FoS"
    ),
    status = replace_values(
      status,
      # `InstructorInfoMissing` probably means a student did no make a request
      "InstructorInfoMissing" ~ "No Accommodation Request",
      "PendingWaitingForStudent" ~ "Pending---Waiting For Student"
    )
  ) |>
  count(course_faculty, status) |>
  gt(
    groupname_col = "course_faculty",
    row_group_as_column = TRUE
  ) |>
  summary_rows(
    columns = n,
    fns = list(label = "Total", id = "total", fn = "sum"),
    missing_text = ""
  ) |>
  fmt_markdown() |>
  tab_stubhead("Faculty offering course") |>
  cols_label(
    status = "Request status",
    n = "FoS enrollments registered with CfA"
  ) |>
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = list(
      cells_column_labels(),
      cells_column_spanners(),
      cells_stub_summary(),
      cells_stubhead()
    )
  )
```

About half of the Faculty of Science students registered with the Centre for Accessibility requested accommodations in lab courses.
All of these requests were approved.
:::

### Subject-level

::: {#fig-requests-by-subject}
```{r}
#| label: requests-by-program
#| echo: false
approved <- lab_requests |>
  filter(in_ubc_v_faculty_of_science) |>
  mutate(
    status = status == "Approved"
  ) |>
  summarize(
    registered_n = n(),
    requests_n = sum(status),
    .by = c(subject)
  )

students_by_subject <- lab_counts |>
  summarize(
    total_enrolled = sum(total_enrolled),
    .by = c(subject)
  )

approved |>
  inner_join(students_by_subject, by = join_by(subject)) |>
  mutate(
    registered_proportion = registered_n / total_enrolled,
    request_proportion = requests_n / total_enrolled
  ) |>
  select(subject, ends_with("proportion")) |>
  pivot_longer(
    ends_with("proportion"),
    names_to = "type",
    names_pattern = "(.*)_proportion",
    values_to = "proportion"
  ) |>
  ggplot(aes(x = proportion, y = fct_rev(subject), fill = type)) +
  geom_bar(position = "identity", stat = "identity", alpha = 0.3) +
  scale_x_continuous(labels = percent) +
  labs(x = "Proportion", y = "Subject")
```

Accomodation requests (all of which were approved) in Faculty of Science (FoS) lab courses by FoS students registered with the Centre for Accessibility (CfA) in each subject.
All numbers are relative to total enrollment in courses.
A single student might be represented multiple times across these data as they might be enrolled in more than one course.
Registered, percentage of FoS students registered with CfA relative to total enrollment; Requests, percentage of FoS students registered with CfA requesting accomodations relative to total enrollment.
:::

### Course-level

I think FoS courses with close to 0 or 100% request rate would be of particular interest.
What does it mean if students do not ask for accomodations?
Are their needs already met?
Or do they feel like they can't ask for anything?
Conversely, when students readily ask for accomodations is it a sign of a class climate that encourages them to make their needs known?
Or does it indicate that things are so dire that they feel compelled to formally make requests to find at least some relief?

I decided to show the data by the number of registered students since extreme values (of 0 or a 100%) are more likely in courses when their number is small.

::: {#fig-requests-by-course}
```{r}
#| label: requests-by-course
#| echo: false
approved <- lab_requests |>
  filter(in_ubc_v_faculty_of_science) |>
  mutate(
    status = status == "Approved"
  ) |>
  summarize(
    registered_n = n(),
    requests_n = sum(status),
    requests_proportion = requests_n / registered_n,
    .by = c(subject, course)
  ) |>
  arrange(subject, course)

overall_requests_proportion <-
  sum(approved$requests_n) /
  sum(approved$registered_n)

approved_by_course <- approved |>
  ggplot(
    aes(
      x = registered_n,
      y = requests_proportion,
      text = glue(
        "{subject} {course}<br>",
        "CfA-registered students: {registered_n}<br>",
        "Requests: {requests_n} ({vec_fmt_percent(requests_proportion)})"
      )
    )
  ) +
  geom_hline(yintercept = overall_requests_proportion, colour = "pink") +
  geom_point(alpha = 0.5) +
  scale_y_continuous(labels = label_percent(suffix = "")) +
  facet_wrap(vars(subject)) +
  theme_minimal() +
  labs(x = "Registered [n]", y = "Requests [%]")

ggplotly(approved_by_course, tooltip = "text")
```

Accomodation requests (all of which were approved) in Faculty of Science (FoS) lab courses by FoS students registered with the Centre for Accessibility (CfA).
Registered \[n\], number of FoS students registered with CfA in a given course; Requests \[%\], percentage of those students requesting accomodations; pink horizontal line, overall percentage (`{r} percent(overall_requests_proportion)`) of those students requesting accommodations across all FoS lab courses.
:::
::::::

## Overall students registered with CFA in FoS laboratory courses

::: {#fig-registered-students-in-fos-labs}
```{r}
#| label: registered-students-in-fos-labs
#| echo: false
cfa_students_in_fos_labs <- lab_counts |>
  inner_join(approved, by = join_by(subject, course)) |>
  mutate(
    non_fos_proportion = (cfa_students_n - registered_n) / total_enrolled,
    fos_proportion = registered_n / total_enrolled
  ) |>
  ggplot(
    aes(
      x = non_fos_proportion,
      y = fos_proportion,
      text = glue(
        "{subject} {course}<br>",
        "Total enrolment: {total_enrolled}<br>",
        "Total CfA-registered students: {cfa_students_n}<br>",
        "FoS CfA-registered students: {registered_n} ",
        "({vec_fmt_percent(fos_proportion)})<br>",
        "Other CfA-registered students: {cfa_students_n - registered_n} ",
        "({vec_fmt_percent(non_fos_proportion)})<br>"
      )
    )
  ) +
  geom_abline(slope = 1, intercept = 0, colour = "grey") +
  geom_point(alpha = 0.5) +
  scale_x_continuous(label = label_percent(suffix = ""), limits = c(0, 0.3)) +
  scale_y_continuous(label = label_percent(suffix = ""), limits = c(0, 0.3)) +
  coord_fixed() +
  facet_wrap(vars(subject)) +
  theme_minimal() +
  labs(
    x = "FoS CfA-registered students [%]",
    y = "CfA-registered students other faculties [%]"
  )

ggplotly(cfa_students_in_fos_labs, tooltip = "text")
```

CfA-registered students in the Faculty of Science (FoS) and other faculties enrolled in FoS laboratory courses.
FoS CfA-registered students \[%\], proportion of FoS CfA-registered students; CfA-registered students other faculties \[%\], proportion of CfA-registered students in other faculties.
Each data point represents one course, and if it is located on or close to the diagonal line, the proportion of CfA-students from within and outside of FoS are about the same.
Courses below the line had more FoS CfA-students than from other faculties, and above the line those with more from other faculties than FoS.
:::
