---
title: "Lab accessibility report"
format:
  html:
    embed-resources: true
---

```{r}
#| label: setup
#| echo: false
#| message: false
library(conflicted)
library(dplyr)
conflicts_prefer(dplyr::filter)
library(fs)
library(ggplot2)
library(glue)
library(gt)
library(plotly)
library(purrr)
library(scales)
library(tidyr)

dir_walk(here::here("R"), source)
```

## Data

### Centre for Accessibility

Data was provided by Michael Segovia, project manager at the Centre for Accessibility (CfA) for working with Skylight.

`students`:

- File: `01_Active Students in Faculty of Science + program info September 2024 - August 2025.xlsx`
- ClockWork data
- Period: September 2024 -- August 2025
- CfA did not start collecting program-related information in their system until mid- to late-2025. As a result, only students who remained active in the CfA system at that time appear in this data snapshot. Students who may have graduated and/or de-activated prior to this snapshot would not be included.
- Entries for students in the Faculty of Science registered with CfA

`lab_requests`:

- File: `02_Students with accommodations in Laboratory sections September 2024 - August 2025.xlsx`
- ClockWork data
- Period: September 2024 -- August 2025
- CfA did not start collecting program-related information in their system until mid- to late-2025. As a result, only students who remained active in the CfA system at that time appear in this data snapshot. Students who may have graduated and/or de-activated prior to this snapshot would not be included.
- Number of students with accommodations registered in at least one course section designated as "Laboratory"
- `status` of student's accommodation letter request
  - `No Accommodation Request` students was eligible for accommodations, but did not download a letter
  - `InstructorInfoMissing` indicates that no instructor record is available for that particular section on Workday (probably equivalent to `No Accommodation Request`, will be interpreted as such in analysis below)

`lab_counts`:

- File: `03_CfA Edits - Science_lab_counts_2024W_2025-07-10.xlsx`
- Number of students with accommodations registered in at least one course section designated as "Laboratory"

```{r}
#| label: load-data
#| echo: false
students <- load_students()
lab_requests <- load_lab_requests()
lab_counts <- load_lab_counts()
```

## Analysis

### FoS students registered with CfA

Because of "Major", "Honours" and many "Combined" programs, there are many different programs resulting from those combinations.

::: {#tbl-students-by-program}
```{r}
#| label: students-by-program
#| echo: false
students |>
  count(program_of_study_name) |>
  mutate(
    program_of_study_name = replace_values(
      program_of_study_name,
      "Bachelor of Science (Vancouver)" ~ "First year B.Sc."
    )
  ) |>
  gt() |>
  cols_label(
    program_of_study_name = "Program",
    n = "FoS students registered with CfA"
  )
```

Faculty of Science students registered with the Centre for Accessibility by program.
:::

I decided to collate the data by program and count a student in a combined program once for each program (for example, a student in "Combined Major in Computer Science, Biology" is counted once for "Computer Science" and once for "Biology".)

::: {#tbl-students-by-collated-program}
```{r}
#| label: students-by-collated-program
#| echo: false
students_n <- nrow(students)
students |>
  select(program_one, program_two) |>
  pivot_longer(
    everything(),
    names_to = NULL,
    values_to = "program",
    values_drop_na = TRUE
  ) |>
  count(program) |>
  mutate(
    percent = n / students_n
  ) |>
  gt() |>
  fmt_percent(columns = percent) |>
  cols_label(
    program = "Program",
    n = "FoS students registered with CfA"
  )
```

Faculty of Science students registered with the Centre for Accessibility by collated program.
:::

### FoS students registered with CfA in laboratory courses

In general, requests for accomodations by FoS students in courses got all approved and the data contains no examples when a request was rejected.

::: {#tbl-requests}
```{r}
#| label: requests
#| echo: false
lab_requests |>
  # filter(in_ubc_v_faculty_of_science) |>
  mutate(
    course_faculty = recode_values(
      in_ubc_v_faculty_of_science,
      TRUE ~ "FoS",
      FALSE ~ "non-FoS"
    ),
    status = replace_values(
      status,
      # `InstructorInfoMissing` probably means a student did no make a request
      "InstructorInfoMissing" ~ "No Accommodation Request",
      "PendingWaitingForStudent" ~ "Pending---Waiting For Student"
    )
  ) |>
  count(course_faculty, status) |>
  gt(
    groupname_col = "course_faculty",
    row_group_as_column = TRUE
  ) |>
  summary_rows(
    columns = n,
    fns = list(label = "Total", id = "total", fn = "sum"),
    missing_text = ""
  ) |>
  fmt_markdown() |>
  tab_stubhead("Faculty offering course") |>
  cols_label(
    status = "Request status",
    n = "FoS enrollments registered with CfA"
  ) |>
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = list(
      cells_column_labels(),
      cells_column_spanners(),
      cells_stub_summary(),
      cells_stubhead()
    )
  )
```

About half of the Faculty of Science students registered with the Centre for Accessibility requested accommodations in lab courses.
All of these requests were approved.
:::

I think FoS courses with close to 0 or 100% request rate would be of particular interest.
What does it mean if students do not ask for accomodations?
Are their needs already met?
Or do they feel like they can't ask for anything?
Conversely, when students readily ask for accomodations is it a sign of a class climate that encourages them to make their needs known?
Or does it indicate that things are so dire that they feel compelled to formally make requests to find at least some relief?

I decided to show the data by the number of registered students since extreme values (of 0 or a 100%) are more likely in courses when their number is small.

::: {#fig-requests-by-course}
```{r}
#| label: requests-by-course
#| echo: false
approved <- lab_requests |>
  filter(in_ubc_v_faculty_of_science) |>
  mutate(
    status = status == "Approved"
  ) |>
  summarize(
    registered_n = n(),
    requests_n = sum(status),
    requests_proportion = requests_n / registered_n,
    .by = c(subject, course)
  ) |>
  arrange(subject, course)

overall_requests_proportion <-
  sum(approved$requests_n) /
  sum(approved$registered_n)

approved_by_course <- approved |>
  ggplot(
    aes(
      x = registered_n,
      y = requests_proportion,
      text = glue(
        "{subject} {course}<br>",
        "CfA-registered students: {registered_n}<br>",
        "Requests: {requests_n} ({vec_fmt_percent(requests_proportion)})"
      )
    )
  ) +
  geom_hline(yintercept = overall_requests_proportion, colour = "pink") +
  geom_point(alpha = 0.5) +
  scale_y_continuous(labels = label_percent(suffix = "")) +
  facet_wrap(vars(subject)) +
  theme_minimal() +
  labs(x = "Registered [n]", y = "Requests [%]")

ggplotly(approved_by_course, tooltip = "text")
```

Accomodation requests (all of which were approved) in Faculty of Science (FoS) lab courses by FoS students registered with the Centre for Accessibility (CfA).
Registered \[n\], number of FoS students registered with CfA in a given course; Requests \[%\], percentage of those students requesting accomodations; pink horizontal line, overall percentage (`{r} percent(overall_requests_proportion)`) of those students requesting accommodations across all FoS lab courses.
:::

### Overall students registered with CFA in FoS laboratory courses

::: {#fig-registered-students-in-fos-labs}
```{r}
#| label: registered-students-in-fos-labs
#| echo: false
lab_counts |>
  inner_join(approved, by = join_by(subject, course)) |>
  mutate(
    non_fos = (cfa_students_n - registered_n) / total_enrolled,
    fos = registered_n / total_enrolled,
    delta = fos - non_fos
  ) |>
  ggplot(aes(x = delta, y = subject)) +
  geom_jitter(height = 0.2, alpha = 0.5) +
  scale_x_continuous(label = label_percent(suffix = ""), limits = c(-1, 1))
```

In Faculty of Science laboratory courses, CfA-registered students from FoS and other faculties are represented in equal measures.
:::
