# Lab accessibility undergraduate survey

```{r}
#| label: setup
#| echo: false
#| message: false
library(conflicted)
library(dplyr)
conflicts_prefer(dplyr::filter)
library(forcats)
library(fs)
library(ggplot2)
library(ggstats)
library(ggtext)
library(gtsummary)
library(labelled)
library(scales)
library(stringr)
library(tidyr)

dir_walk(here::here("R"), source)
survey <- load_undergraduate_lab_accessibility_survey()
```

## Program area and progress

The following data show program information of students who participated in the survey.
It would be of interest to get total student numbers in each program to see if the survey is a representative sample.

::::::: panel-tabset
### Plot

::::: {#fig-program-area-and-progress layout="[[1], [1]]"}
::: {#fig-program-area}
```{r}
#| label: program-area
#| echo: false
survey |>
  render_lollipop_graph(program)
```

Program area
:::

::: {#fig-program-progress}
```{r}
#| label: program-progress
#| echo: false
survey |>
  render_lollipop_graph(course_level_focus)
```

Program progress
:::

[Program area and progress (using course level as proxy) of participants in the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026. The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS). Percentages give the proportion of survey participants.]{#program-area-and-progress}
{{< contents program-area-and-progress >}} Figure of the same data as in @tbl-program-area-and-progress.
:::::

### Table

::: {#tbl-program-area-and-progress}
```{r}
#| label: program-area-and-progress-table
#| echo: false
survey |>
  select(program, course_level_focus) |>
  tbl_summary(include = c(program, course_level_focus))
```

{{< contents program-area-and-progress >}} Table of the same data as in @fig-program-area-and-progress.
:::
:::::::

## Climate in laboratory courses

::::: panel-tabset
### Likert

::: {#fig-lab-climate-likert}
```{r}
#| label: lab-climate-likert
#| echo: false
survey |>
  select(q4, q40, q41, q43, q44) |>
  # TODO: Add N for each question
  update_variable_labels_with(\(column_name) {
    str_remove(
      column_name,
      paste0(
        "3[a-f]\\. Please indicate to what extent you agree with the following ",
        "statement:(\\n){3,4}"
      )
    )
  }) |>
  gglikert(y_label_wrap = 35) +
  theme(legend.location = "plot")
```

Climate in laboratory courses.
Questions focusing on inclusion and belonging in the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::

### Coded

::: {#fig-lab-climate-coded}
```{r}
#| label: lab-climate-coded
#| echo: false
climate_coded <- survey |>
  separate_longer_delim(q33, "; ") |>
  filter_out(is.na(q33)) |>
  mutate(q33 = fct_infreq(q33))

climate_coded_question <- var_label(survey$q33) |> str_remove("4\\. ")
climate_top_5 <- climate_coded |>
  count(q33)

climate_coded |>
  render_lollipop_graph(q33) +
  labs(title = climate_coded_question, x = "Frequency [n]", y = NULL) +
  theme(plot.title = element_textbox_simple(), plot.title.position = "plot")
```

Coded open-ended responses to the question "`{r} climate_coded_question`".
"`{r} climate_top_5$q33[1]`" was the most frequently coded ($n$ = `{r} climate_top_5$n[1]`), followed by "`{r} climate_top_5$q33[2]`" ($n$ = `{r} climate_top_5$n[2]`) and "`{r} climate_top_5$q33[3]`" ($n$ = `{r} climate_top_5$n[3]`).
Several challenges were also identified, including "`{r} climate_top_5$q33[4]`" ($n$ = `{r} climate_top_5$n[4]`) and "`{r} climate_top_5$q33[5]`" ($n$ = `{r} climate_top_5$n[5]`).
Less frequently reported codes captured negative or situational experiences such as unclear assessment, accessibility challenges, and group work dynamics (codebook see @tbl-lab-climate-codebook).
The question was part of the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::
:::::

## Accomodation needs

::::: panel-tabset
### General

::: {#fig-accomodation-needs}
```{r}
#| label: accomodations-needs
#| echo: false
survey |>
  select(response_id, q6, q6_9_text) |>
  separate_longer_delim(q6, delim = regex(",(?! )")) |>
  mutate(
    q6_9_text = if_else(
      str_detect(
        q6_9_text,
        # TODO: Check with team about categorization of conditions in "Other"
        "pain|cold|hyperhydrosis|scoliosis|Tremor"
      ),
      paste0(
        "Chronic health condition (e.g., Diabetes, MS, POTS, ",
        "immunocompromised, Chronic Fatigue Syndrome, etc.)"
      ),
      q6_9_text
    ),
    q6 = if_else(q6 == "Other, please specify:", q6_9_text, q6)
  ) |>
  filter_out(is.na(q6)) |>
  distinct(response_id, q6) |>
  copy_labels_from(survey) |>
  render_lollipop_graph(q6) +
  scale_y_discrete(labels = label_wrap(50)) +
  labs(
    title = survey$q6 |>
      var_label() |>
      str_remove_all("5. | \\(Select all that apply\\) - Selected Choice"),
    x = "Respondents [n]",
    y = NULL
  ) +
  theme(plot.title = element_textbox_simple(), plot.title.position = "plot")
```

Participant responses to the multiple selection question "`{r} survey$q6 |> var_label() |> str_remove_all("5. | \\(Select all that apply\\) - Selected Choice")`" in the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::

### Other

::: {#fig-other-accomodation-needs}
```{r}
#| label: other-accomodations-needs
#| echo: false
survey |>
  select(response_id, q7, q7_4_text) |>
  separate_longer_delim(q7, delim = regex(",(?! )")) |>
  mutate(
    q7_4_text = replace_when(
      q7_4_text,
      # TODO: Check with team about categorization of conditions in "Other"
      str_detect(q7_4_text, "Sickness") ~
        "Temporary condition (e.g., Broken bone, injury)",
      str_detect(q7_4_text, "Height|processing|Chronic|Gender|n/a") ~ NA
    ),
    q7 = if_else(q7 == "Other, please specify:", q7_4_text, q7)
  ) |>
  filter_out(is.na(q7)) |>
  distinct(response_id, q7) |>
  copy_labels_from(survey) |>
  render_lollipop_graph(q7) +
  scale_y_discrete(labels = label_wrap(50)) +
  labs(
    title = survey$q7 |>
      var_label() |>
      str_remove_all("6. | \\(Select all that apply\\) - Selected Choice"),
    x = "Respondents [n]",
    y = NULL
  ) +
  theme(plot.title = element_textbox_simple(), plot.title.position = "plot")
```

Participant responses to the multiple selection question "`{r} survey$q7 |> var_label() |> str_remove_all("6. | \\(Select all that apply\\) - Selected Choice")`" in the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::
:::::

## Major and Centre of Accessibility

::::: panel-tabset
### Table

::: {#tbl-major-and-cfa}
```{r}
#| label: major-and-cfa
#| echo: false
survey |>
  select(q8, q10) |>
  filter_out(is.na(q8), is.na(q10)) |>
  update_variable_labels_with(\(column_name) {
    str_remove(column_name, "[a-f]\\. ")
  }) |>
  tbl_summary(include = c(q8, q10))
```

Participant responses in the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::

### Coded

::: {#fig-major-coded}
```{r}
#| label: major-coded
#| echo: false
major_coded <- survey |>
  separate_longer_delim(q9, "; ") |>
  filter_out(is.na(q9)) |>
  mutate(q9 = fct_infreq(q9))

major_coded_question <- var_label(survey$q9) |> str_remove("b\\. ")
major_top_5 <- major_coded |>
  count(q9)

major_coded |>
  render_lollipop_graph(q9) +
  labs(title = major_coded_question, y = NULL) +
  theme(plot.title = element_textbox_simple(), plot.title.position = "plot")
```

Coded open-ended responses to the question "`{r} major_coded_question`".
"`{r} major_top_5$q9[1]`" emerges as the most common code ($n$ = `{r} major_top_5$n[1]`).
Other codes appeared infrequently, inlcuding "`{r} major_top_5$q9[2]`" ($n$ = `{r} major_top_5$n[2]`), "`{r} major_top_5$q9[3]`" ($n$ = `{r} major_top_5$n[3]`), "`{r} major_top_5$q9[4]`" ($n$ = `{r} major_top_5$n[4]`) and "`{r} major_top_5$q9[5]`" ($n$ = `{r} major_top_5$n[5]`; codebook see @tbl-major-codebook).
The question was part of the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::
:::::

## Sense of belonging

::: {#fig-major-belonging}
```{r}
#| label: major-belonging
#| echo: false
survey |>
  select(starts_with("q16")) |>
  # TODO: Add N for each question
  update_variable_labels_with(\(column_name) {
    str_remove(
      column_name,
      paste0(
        "d. Please indicate to what extent you agree with the following ",
        "statements:\n\nIn my current or intended major, - "
      )
    )
  }) |>
  gglikert(y_label_wrap = 35) +
  labs(title = "In my current or intended major,") +
  theme(
    plot.title.position = "plot",
    legend.location = "plot"
  )
```

Participant responses to questions about their sense of belonging in the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::

## Barriers

::::::: panel-tabset
### Delivery

::: {#fig-delivery}
```{r}
#| label: delivery
#| echo: false
survey |>
  select(starts_with("q11")) |>
  render_barriers()
```

Participant responses to questions about course delivery barriers in lab courses in the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::

### Environment

::: {#fig-environment}
```{r}
#| label: environment
#| echo: false
survey |>
  select(starts_with("q30")) |>
  render_barriers()
```

Participant responses to questions about environmental barriers in lab courses in the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::

### Demands

::: {#fig-demands}
```{r}
#| label: demands
#| echo: false
survey |>
  select(starts_with("q31")) |>
  render_barriers()
```

Participant responses to questions about course demands in lab courses in the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::

### Coded

::: {#fig-barriers-coded}
```{r}
#| label: barriers-coded
#| echo: false
barriers_coded <- survey |>
  separate_longer_delim(q12, "; ") |>
  filter_out(is.na(q12)) |>
  mutate(q12 = fct_infreq(q12))

barriers_coded_question <- var_label(survey$q12) |> str_remove("8\\. ")
barriers_top_5 <- barriers_coded |>
  count(q12)

# barriers_coded |>
#   render_lollipop_graph(q12) +
#   labs(title = barriers_coded_question, x = "Frequency [n]", y = NULL) +
#   theme(plot.title = element_textbox_simple(), plot.title.position = "plot")
```

<!-- TODO: Add qualitative analysis of Q12 -->

Coded open-ended responses to the question "`{r} barriers_coded_question`".
"`{r} barriers_top_5$q12[1]`" ($n$ = `{r} barriers_top_5$n[1]`), followed by "`{r} barriers_top_5$q12[2]`" ($n$ = `{r} barriers_top_5$n[2]`) and "`{r} barriers_top_5$q12[3]`" ($n$ = `{r} barriers_top_5$n[3]`).
"`{r} barriers_top_5$q12[4]`" ($n$ = `{r} barriers_top_5$n[4]`) and "`{r} barriers_top_5$q12[5]`" ($n$ = `{r} barriers_top_5$n[5]`) (codebook see @tbl-barriers-codebook).
The question was part of the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::
:::::::

## Supports

::::: panel-tabset
### Ranking

::: {#fig-supports}
```{r}
#| label: supports
#| echo: false
#| fig-height: 7
survey |>
  select(matches("q13_[1-7]$")) |>
  # TODO: Add N for each question
  update_variable_labels_with(\(column_name) {
    wrap = 35

    preamble <- paste0(
      "9\\. From the following list of resources, supports and modifications, ",
      "which ones have you experienced and found helpful to enable you to ",
      "fully participate in laboratory activities\\? \\(Select all that ",
      "apply\\)\n\nNo Experience: I have not experienced this\nHad it, Not ",
      "helpful:  I have experienced this but did not find it helpful\nHad it, ",
      "helpful: I have experienced this and found it helpful - "
    )

    element <- column_name |>
      str_remove(preamble)

    category <- element |>
      str_extract(".*?(?=\\s*\\()") |>
      str_wrap(width = wrap)
    examples <- element |>
      str_remove(".*?\\s*(?=\\()") |>
      str_wrap(width = wrap)

    if (is.na(category)) {
      return(paste0("**", examples, "**"))
    }

    paste0("**", category, "**\n", examples) |>
      str_replace_all("\n", "<br>")
  }) |>
  gglikert(
    cutoff = 0,
    add_totals = FALSE
  ) +
  labs(
    title = paste0(
      "From the following list of resources, supports and modifications, ",
      "which ones have you experienced and found helpful to enable you to ",
      "fully participate in laboratory activities?"
    )
  ) +
  theme(
    plot.title = element_textbox_simple(),
    plot.title.position = "plot",
    axis.text.y = element_markdown(),
    legend.location = "plot"
  )
```

Participant responses to questions about experience with supports in lab courses in the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::

### Coded

::: {#fig-supports-coded}
```{r}
#| label: supports-coded
#| echo: false
supports_coded <- survey |>
  separate_longer_delim(q14, "; ") |>
  filter_out(is.na(q14)) |>
  mutate(q14 = fct_infreq(q14))

supports_coded_question <- var_label(survey$q14) |> str_remove("10\\. ")
supports_top_5 <- supports_coded |>
  count(q14)

supports_coded |>
  render_lollipop_graph(q14) +
  labs(title = supports_coded_question, x = "Frequency [n]", y = NULL) +
  theme(plot.title = element_textbox_simple(), plot.title.position = "plot")
```

Coded open-ended responses to the question "`{r} supports_coded_question`".
The most commonly reported codes were "`{r} supports_top_5$q14[1]`" ($n$ = `{r} supports_top_5$n[1]`), followed by "`{r} supports_top_5$q14[2]`" ($n$ = `{r} supports_top_5$n[2]`).
Flexibility-related supports, including "`{r} supports_top_5$q14[3]`" ($n$ = `{r} supports_top_5$n[3]`), were also frequently mentioned.
Less common codes reflected specific challenges or environmental factors, such as academic pressure, stigma around accommodations, and lab climate (codebook see @tbl-supports-codebook).
The question was part of the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::
:::::

## General

::::: panel-tabset
### Positive examples

::: {#fig-examples-coded}
```{r}
#| label: examples-coded
#| echo: false
examples_coded <- survey |>
  separate_longer_delim(q15, "; ") |>
  filter_out(is.na(q15)) |>
  mutate(q15 = fct_infreq(q15))

examples_coded_question <- var_label(survey$q15) |> str_remove("11\\. ")
examples_top_5 <- examples_coded |>
  count(q15)

examples_coded |>
  render_lollipop_graph(q15) +
  labs(title = examples_coded_question, x = "Frequency [n]", y = NULL) +
  theme(plot.title = element_textbox_simple(), plot.title.position = "plot")
```

Coded open-ended responses to the question "`{r} examples_coded_question`".
"`{r} examples_top_5$q15[1]`" was the most prominent code ($n$ = `{r} examples_top_5$n[1]`), far exceeding all other codes.
Additional frequently reported supports included "`{r} examples_top_5$q15[2]`" ($n$ = `{r} examples_top_5$n[2]`), "`{r} examples_top_5$q15[3]`" ($n$ = `{r} examples_top_5$n[3]`) and "`{r} examples_top_5$q15[4]`" ($n$ = `{r} examples_top_5$n[4]`).
Clear expectations, flexible accommodations, and hands-on learning were also commonly noted (codebook see @tbl-examples-codebook).
The question was part of the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::

### Advice

::: {#fig-advice-coded}
```{r}
#| label: advice-coded
#| echo: false
advice_coded <- survey |>
  separate_longer_delim(q34, "; ") |>
  filter_out(is.na(q34)) |>
  mutate(q34 = fct_infreq(q34))

advice_coded_question <- var_label(survey$q34) |> str_remove("12\\. ")
advice_top_5 <- advice_coded |>
  count(q34)

advice_coded |>
  render_lollipop_graph(q34) +
  labs(title = advice_coded_question, x = "Frequency [n]", y = NULL) +
  theme(plot.title = element_textbox_simple(), plot.title.position = "plot")
```

Coded open-ended responses to the question "`{r} advice_coded_question`".
"`{r} advice_top_5$q34[1]`" ($n$ = `{r} advice_top_5$n[1]`) and "`{r} advice_top_5$q34[2]`" ($n$ = `{r} advice_top_5$n[2]`) identified most frequently.
"`{r} advice_top_5$q34[3]`" ($n$ = `{r} advice_top_5$n[3]`), "`{r} advice_top_5$q34[4]`" ($n$ = `{r} advice_top_5$n[4]`) and "`{r} advice_top_5$q34[5]`" ($n$ = `{r} advice_top_5$n[5]`) were also commonly reported (codebook see @tbl-advice-codebook).
The question was part of the "Lab accessibility in Science---undergraduate student survey" conducted by Skylight in March 2026.
The target population was undergraduate students during September 2025 to April 2026 in the Faculty of Science (FoS).
:::
:::::
