---
title: "Lab accessibility report"
format: html
---

```{r}
#| label: setup
#| echo: false
#| message: false
library(dplyr)
library(fs)
library(gt)
library(purrr)
library(tidyr)

dir_walk(here::here("R"), source)
```

## Data

### Centre for Accessibility

Data was provided by Michael Segovia, project manager at the Centre for Accessibility (CfA) for working with Skylight.

`students`:

- File: `01_Active Students in Faculty of Science + program info September 2024 - August 2025.xlsx`
- ClockWork data
- Period: September 2024 -- August 2025
- CfA did not start collecting program-related information in their system until mid- to late-2025. As a result, only students who remained active in the CfA system at that time appear in this data snapshot. Students who may have graduated and/or de-activated prior to this snapshot would not be included.
- Entries for students in the Faculty of Science registered with CfA

`lab_requests`:

- File: `02_Students with accommodations in Laboratory sections September 2024 - August 2025.xlsx`
- ClockWork data
- Period: September 2024 -- August 2025
- CfA did not start collecting program-related information in their system until mid- to late-2025. As a result, only students who remained active in the CfA system at that time appear in this data snapshot. Students who may have graduated and/or de-activated prior to this snapshot would not be included.
- Number of students with accommodations registered in at least one course section designated as "Laboratory"
- `status` of student's accommodation letter request
  - `No Accommodation Request` students was eligible for accommodations, but did not download a letter
  - `InstructorInfoMissing` indicates that no instructor record is available for that particular section on Workday (probably equivalent to `No Accommodation Request`, will be interpreted as such in analysis below)

`lab_counts`:

- File: `03_CfA Edits - Science_lab_counts_2024W_2025-07-10.xlsx`
- Number of students with accommodations registered in at least one course section designated as "Laboratory"

```{r}
#| label: load-data
#| echo: false
students <- load_students()
lab_requests <- load_lab_requests()
lab_counts <- load_lab_counts()
```

## Analysis

### FoS students registered with CfA

Because of "Major", "Honours" and many "Combined" programs, there are many different programs resulting from those combinations.

::: {#tbl-students-by-program}
```{r}
#| label: students-by-program
#| echo: false
students |>
  count(program_of_study_name) |>
  mutate(
    program_of_study_name = replace_values(
      program_of_study_name,
      "Bachelor of Science (Vancouver)" ~ "First year B.Sc."
    )
  ) |>
  gt() |>
  cols_label(
    program_of_study_name = "Program",
    n = "FoS students registered with CfA"
  )
```

Faculty of Science students registered with the Centre for Accessibility by program.
:::

I decided to collate the data by program and count a student in a combined program once for each program (for example, a student in "Combined Major in Computer Science, Biology" is counted once for "Computer Science" and once for "Biology".)

::: {#tbl-students-by-collated-program}
```{r}
#| label: students-by-collated-program
#| echo: false
students_n <- nrow(students)
students |>
  select(program_one, program_two) |>
  pivot_longer(
    everything(),
    names_to = NULL,
    values_to = "program",
    values_drop_na = TRUE
  ) |>
  count(program) |>
  mutate(
    percent = n / students_n
  ) |>
  gt() |>
  fmt_percent(columns = percent) |>
  cols_label(
    program = "Program",
    n = "FoS students registered with CfA"
  )
```

Faculty of Science students registered with the Centre for Accessibility by collated program.
:::
